Illustrating Good Practice in {\LaTeX}

### 2022-02-03 articles/good_practice.tex
serious changes underway
cleaning up
unironically bloat
oof
close error log with le
future proofing good practice
holding
big changes coming soon

@@

\title{Illustrating Good Practice in {\LaTeX}}
\author{Nicholas D. Kostin}
\date{October 2021}

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}
\lhead{Illustrating Good Practice in {\LaTeX}}
\rhead{Nicholas D. Kostin}
\lfoot{\texttt{https://nkostin.xyz}}
\rfoot{\thepage\ of \pageref{LastPage}}

@@

This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist. Instead, what follows is an incoherent collection of examples that illustrate good practice. For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.

>>>>

% Number equations within sections
\numberwithin{equation}{section}

@@

\title{Illustrating Good Practice in {\LaTeX}}
\author{Nicholas D. Kostin}
\date{March 2022}

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}
\lhead{Illustrating Good Practice in {\LaTeX}}
\rhead{Nicholas D. Kostin}
\lfoot{\texttt{https://nkostin.com}}
\rfoot{\thepage\ of \pageref{LastPage}}

@@

This document is not a guide on how to use {\LaTeX}, since plenty of those already exist. Instead, what follows is an incoherent collection of examples that demonstrate good practice. For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.
